Extracting data for time slice analyses

### 2017-11-27 analyses/01-extract-data-for-analyses.Rmd
updated function/arguments names for 0.4.2
Remove FAD LAD - it isn't needed til the analyses
Remove FAD LADs and ordination code

Quick pipeline for getting data from discrete matrices.
===============

@@

## Loading the FADLAD
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)

@@

```{r}
slug <- "Wright2017"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

@@

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length * 0.03517385

@@

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slug,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
# Note that these are the upper bound for FAD and lower bound for LAD
tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

## Ordinating the matrix - no need to run this here, we will do this in the next script
## load(paste0("../data/processed/distance_matrix.", slugs[slug] ,".Rda"))
## morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points
```

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
FADLAD <- read.csv(paste0("../data/FADLAD/", slug, ".csv"), row.names = 1, header = TRUE)
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

>>>>

Pipeline for getting data from discrete matrices.
===============

@@

@@

```{r}
source("../functions/tree.age.fossil.R")

slug <- "Wright2017"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

@@

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length / 0.03517385

@@

```

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

```

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))
